\documentclass[8pt]{extarticle}

\input{assets/prelude.tex}

\pbClass{Bard}
\pbBaseHP{6}
\pbDamage{6}

\pbNames{Elf}{Astrafel, Daelwyn, Feliana, Damarra, Sistranalle,
  Pendrell, Melliandre, Dagoliir}

\pbNames{Human}{Baldric, Leena, Dunwick, Willem, Edwyn, Florian,
  Seraphine, Quorra, Charlotte, Lily, Ramonde, Cassandra}

\pbNames{Rihamm}{Albis, Quren, Ulduqan, Ebresa, Yudrus, Depremm,
  Rubuqin, Umas, Elqorim}

\pbLook{Knowing Eyes, Fiery Eyes, or Joyous Eyes}
\pbLook{Fancy Hair, Wild Hair, or Stylish Cap}
\pbLook{Finery, Traveling Clothes, or Poor Clothes}
\pbLook{Fit Body, Well-fed Body, or Thin Body}


\begin{document}

\charbanner

\begin{minipage}[t]{3.2in}
  \leftbanner{Folk}


\begin{optfeature}{Elf}
  When you enter an important location (your call) you can ask the GM
  for one fact from the history of that location.
\end{optfeature}

\begin{optfeature}{Human}
  When you first enter a civilized settlement someone who respects the
  custom of hospitality to minstrels will take you in as their guest.
\end{optfeature}

\begin{optfeature}{Rihamm}
  When you use \move{Charming and Friendly} with someone, ask them two
  questions instead of one.
\end{optfeature}

\leftbanner{Alignment}

\begin{optfeature}{Good}
  Perform your art to aid someone else.
\end{optfeature}

\begin{optfeature}{Neutral}
  Avoid a conflict or defuse a tense situation.
\end{optfeature}

\begin{optfeature}{Chaotic}
  Spur others to significant and unplanned decisive action.
\end{optfeature}

\leftbanner{Bonds}
\vfill\null

\end{minipage}
\begin{minipage}[t]{4.6in}

\rightbanner{Starting Moves}

\begin{basicmove}{Arcane Art}
  When you \condition{weave a performance into a basic spell}, choose
  an ally and an effect:

  \begin{itemize}
  \item Heal 1d8 damage
  \item \forward{+1d4} to damage
  \item Their mind is shaken clear of one enchantment
  \item The next time someone successfully assists the target with
    aid, they get +2 instead of +1
  \end{itemize}

  Then roll +CHA. \onSuccess, the ally gets the selected
  effect. \onPartial, your spell still works, but you draw unwanted
  attention or your magic reverberates to other targets affecting them
  as well, GM’s choice.
\end{basicmove}
\

\begin{basicmove}{Bardic Lore}
  Choose an area of expertise:

  \begin{choices}
  \item Spells and Magicks
  \item The Dead and Undead
  \item Grand Histories of the Known World
  \item A Bestiary of Creatures Unusual
  \item The Planar Spheres
  \item Legends of Heroes Past
  \item Gods and Their Servants
  \end{choices}

  When you \condition{first encounter an important creature, location,
    or item (your call) covered by your bardic lore} you can ask the
  GM any one question about it; the GM will answer truthfully. The GM
  may then ask you what tale, song, or legend you heard that
  information in.
\end{basicmove}
\

\begin{basicmove}{Charming and Open}
  When you \condition{speak frankly with someone}, you can ask their
  player a question from the list below. They must answer it
  truthfully, then they may ask you a question from the list (which
  you must answer truthfully).

  \begin{itemize}
  \item Whom do you serve?
  \item What do you wish I would do?
  \item How can I get you to \blank?
  \item What are you really feeling right now?
  \item What do you most desire?
  \end{itemize}

\end{basicmove}
\

\begin{basicmove}{A Port in the Storm}
    When you \condition{arrive at a civilized settlement spoken of in
      lore or song}, tell the GM something you've heard about the
    place. They’ll tell you how it’s changed since the Shattering.
\end{basicmove}


\vfill\null
\end{minipage}

\charlower
\clearpage

\gearbanner

\begin{multicols}{2}

\begin{quote}
  \yourLoad{9}. You have dungeon rations (\ntag{5}{uses},
  \ntag{1}{weight}). Choose one instrument, all are \ntag{0}{weight}
  for you:

  \begin{choices}
  \item Your father’s mandolin, repaired
  \item A fine lute, a gift from a noble
  \item The pipes with which you courted your first love
  \item A stolen horn
  \item A fiddle, never before played
  \item A songbook in a forgotten tongue
  \end{choices}

\end{quote}
\vfill\null

\ 

\columnbreak
\begin{quote}
  Choose your clothing:

  \begin{choices}
  \item Leather armor (\armor{1}, \weight{1})
  \item Ostentatious clothes (\weight{0})
  \end{choices}

  Choose your armament:

  \begin{choices}
  \item Dueling rapier (\itag{close}, \itag{precise}, \ntag{2}{weight})
  \item Worn bow (\itag{near}, \ntag{2}{weight}), bundle of arrows
    (\ntag{3}{ammo}, \itag{1 weight}), and short sword (\itag{close},
    \ntag{1}{weight})
  \end{choices}

  Choose one:

  \begin{choices}
  \item Adventuring gear (\ntag{1}{weight})
  \item Bandages (\ntag{0}{weight})
  \item Halfling pipeleaf (\ntag{0}{weight})
  \item 3 coins
  \end{choices}

\end{quote}

\end{multicols}

\widebanner{Advanced Moves}

\begin{multicols}{2}
\firstAdvances

\begin{amove}{Healing Song}
  When you \condition{heal with \move{Arcane Art}}, you heal +1d8
  damage.
\end{amove}

\begin{amove}{Vicious Cacophony}
  When you \condition{grant bonus damage with \move{Arcane Art}}, you
  grant an extra +1d4 damage.
\end{amove}

\begin{amove}{It Goes To Eleven}
  When you \condition{unleash a crazed performance} (a righteous lute
  solo or mighty brass blast, maybe) choose a target who can hear you
  and roll +CHA. \onSuccess, the target attacks their nearest ally in
  range. \onPartial, they attack their nearest ally, but you also draw
  their attention and ire.
\end{amove}


\begin{amove}{Metal Hurlant}
  When you \condition{shout with great force or play a shattering
    note} choose a target and roll +CON. \onSuccess, the target takes
  1d10 damage and is deafened for a few minutes. \onPartial, you still
  damage your target, but it’s out of control: the GM will choose an
  additional target nearby.
\end{amove}


\begin{amove}{A Little Help From My Friends}
  When you \condition{successfully aid someone} you take \forward{+1} as
  well.
\end{amove}


\begin{amove}{Eldritch Tones}
  Your \move{Arcane Art} is strong, allowing you to choose two effects
  instead of one.
\end{amove}


\begin{amove}{Duelist’s Parry}
  When you \move{Hack and Slash}, you take \armorForward{+1}.
\end{amove}

\begin{amove}{Bamboozle}
  \onPartialFor{Parley}, you also take \forward{+1} with them.
\end{amove}


\begin{amove}{Multiclass Dabbler}
  Get one move from another class. Treat your level as one lower for
  choosing the move.
\end{amove}


\begin{amove}{Multiclass Initiate}
  Get one move from another class. Treat your level as one lower for
  choosing the move.
\end{amove}

\vfill\null
\columnbreak

\secondAdvances

\begin{amove}{Healing Chorus}
\moveReplaces{Healing Song}

  When you \condition{heal with \move{Arcane Art}}, you heal +2d8 damage.
\end{amove}


\begin{amove}{Vicious Blast}
\moveReplaces{Vicious Cacophony}

  When you \condition{grant bonus damage with \move{Arcane Art}}, you
  grant an extra +2d4 damage.
\end{amove}


\begin{amove}{Unforgettable Face}
  When you \condition{meet someone you’ve met before} (your call)
  after some time apart you take \forward{+1} against them.
\end{amove}


\begin{amove}{Reputation}
  When you \condition{first meet someone who’s heard songs about you},
  roll +CHA. \onSuccess, tell the GM two things they’ve heard about
  you. \onPartial, tell the GM one thing they’ve heard, and the GM
  tells you one thing.
\end{amove}


\begin{amove}{Eldritch Chord}
\moveReplaces{Eldritch Tones}

  When you use \move{Arcane Art}, you choose two effects. You also get to
  choose one of those effects to double.
\end{amove}


\begin{amove}{An Ear For Magic}
  When you \condition{hear an enemy cast a spell} the GM will tell you
  the name of the spell and its effects. Take \forward{+1} when acting
  on the answers.
\end{amove}


\begin{amove}{Devious}
  When you use \move{Charming and Open} you may also ask “How are you
  vulnerable to me?” Your subject may not ask this question of you.
\end{amove}


\begin{amove}{Duelist’s Block}
\moveReplaces{Duelist’s Parry}

  When you \move{Hack and Slash}, you take \armorForward{+2}.
\end{amove}


\begin{amove}{Con}
  \moveReplaces{Bamboozle}

  \onPartialFor{Parley}, you also take \forward{+1} with them and get
  to ask their player one question which they must answer truthfully.
\end{amove}


\begin{amove}{Multiclass Master}
  Get one move from another class. Treat your level as one lower for
  choosing the move.
\end{amove}

\vfill\null
\end{multicols}

\end{document}
