\documentclass[8pt]{extarticle}
\input{assets/prelude}

\pbClass{Druid}
\pbBaseHP{6}
\pbDamage{6}

\pbNames{Elf}{Hycorax, Ethanwe, Sinathel, Demanor, Menoliir,
  Mithralan, Taeros, Aegor}
\pbNames{Halfling}{Tanner, Dunstan, Rose, Ivy, Robard, Mab, Thistle,
  Puck, Anne, Serah}
\pbNames{Human}{Elana, Obelis, Herran, Syla, Andanna, Siobhan, Aziz,
  Pelin, Sibel, Nils, Wei}

\pbLook{Wise Eyes, Wild Eyes, or Haunting Eyes}
\pbLook{Furry Hood, Messy Hair, or Braided Hair}
\pbLook{Ceremonial Garb, Practical Leathers, or Weathered Hides}

\begin{document}

\charbanner

\begin{minipage}[t]{3.2in}

\leftbanner{Folk}

\begin{optfeature}{Elf}
  The sap of the elder trees flows within you. In addition to any
  other attunements, the Great Forest is always considered your land.
\end{optfeature}

\begin{optfeature}{Human}
  As your people learned to bind animals to field and farm, so too are
  you bound to them. You may always take the shape of any domesticated
  animal, in addition to your normal options.
\end{optfeature}

\begin{optfeature}{Halfling}
  You sing the healing songs of spring and brook. When you \move{Make
    Camp}, you and your allies heal +1d6.
\end{optfeature}

\ 

\leftbanner{Alignment}

\begin{optfeature}{Chaotic}
  Destroy a symbol of civilization.
\end{optfeature}

\begin{optfeature}{Good}
  Help something or someone grow.
\end{optfeature}

\begin{optfeature}{Neutral}
  Eliminate an unnatural menace.
\end{optfeature}


\ x

\leftbanner{Bonds}

\vfill\null
\end{minipage}
\begin{minipage}[t]{4.6in}
\rightbanner{Starting Moves}

\begin{basicmove}{Born of the Soil}

  You learned your magic in a place whose spirits are strong and
  ancient and they’ve marked you as one of their own. No matter where
  you go, they live within you and allow you to take their
  shape. Choose one of the following. It is the land to which you are
  attuned—when shapeshifting you may take the shape of any animal who
  might live in your Land.

\begin{multicols}{2}
  \begin{choices}
  \item The Great Forests
  \item The Whispering Plains
  \item The Vast Desert
  \item The Stinking Mire
  \item The River Delta
  \item The Depths of the Earth
  \end{choices}
  \columnbreak
  \begin{choices}
  \item The Sapphire Islands
  \item The Open Sea
  \item The Towering Mountains
  \item The Frozen North
  \item The Blasted Wasteland
  \end{choices}
\end{multicols}

    Chose a tell—a physical attribute that marks you as born of the
    soil—that reflects the spirit of your land. It may be an animal
    feature like antlers or leopard’s spots or something more general:
    hair like leaves or eyes of glittering crystal. Your tell remains
    no matter what shape you take.
\end{basicmove}
\

\begin{basicmove}{By Nature Sustained}
  You don’t need to eat or drink. If a move tells you to mark off a
  ration just ignore it.
\end{basicmove}
\

\begin{basicmove}{Spirit Tongue}
  The grunts, barks, chirps, and calls of the creatures of the wild
  are as language to you. You can understand any animal native to your
  land or akin to one whose essence you have studied.
\end{basicmove}
\

\begin{basicmove}{Shapeshifter}
  When you \condition{call upon the spirits to change your shape},
  roll +WIS. \onSuccess, hold 3. \onPartial, hold 2. \onMiss, hold 1
  in addition to whatever the GM says.

  You may take on the physical form of any species whose essence you
  have studied or who lives in your land: you and your possessions
  meld into a perfect copy of the species’ form. You have any innate
  abilities and weaknesses of the form: claws, wings, gills, breathing
  water instead of air. You still use your normal stats but some moves
  may be harder to trigger—a housecat will find it hard to do battle
  with an ogre. The GM will also tell you one or more moves associated
  with your new form. Spend 1 hold to make that move. Once you’re out
  of hold, you return to your natural form. At any time, you may spend
  all your hold and revert to your natural form.
\end{basicmove}
\

\begin{basicmove}{Studied Essence}
  When you \condition{spend time in contemplation of an animal
    spirit}, you may add its species to those you can assume using
  \move{Shapeshifter}.
\end{basicmove}


\vfill\null
\end{minipage}

\charlower
\clearpage

\gearbanner

\begin{multicols}{2}

  \begin{quote}
    \yourLoad{6}. You carry some token of your land, describe
    it. Choose your defenses:
    \begin{choices}
    \item Hide armor (\ntag{1}{armor}, \ntag{1}{weight})
    \item Wooden shield (\ntag{+1}{armor}, \ntag{1}{weight})
    \end{choices}

    Choose your armament:

    \begin{choices}
    \item Shillelagh (\itag{close}, \ntag{2}{weight})
    \item Staff (\itag{close}, \itag{two-handed}, \ntag{1}{weight})
    \item Spear (\itag{close}, \itag{thrown}, \itag{near},
      \ntag{1}{weight})
    \end{choices}

    Choose one:

    \begin{choices}
    \item Adventuring gear (\ntag{1}{weight})
    \item Poultices and herbs (\ntag{2}{uses}, \ntag{1}{weight})
    \item Halfling pipeleaf (\ntag{0}{weight})
    \item 3 antitoxin (\ntag{0}{weight})
    \end{choices}
\end{quote}

\ 

\columnbreak

\ 

\end{multicols}

\widebanner{Advanced Moves}

\begin{multicols}{2}

\firstAdvances

\begin{amove}{Hunter’s Brother}
  Choose one move from the ranger class list.
\end{amove}

\begin{amove}{Red of Tooth and Claw}
  When you are in an appropriate animal form (something dangerous)
  increase your damage to d8.
\end{amove}

\begin{amove}{Communion of Whispers}
  When you \condition{spend time in a place, making note of its
    resident spirits and calling on the spirits of the land}, roll
  +WIS. You will be granted a vision of significance to you, your
  allies, and the spirits around you. \onSuccess, the vision will be
  clear and helpful to you. \onPartial, the vision is unclear, its
  meaning murky. \onMiss, the vision is upsetting, frightening, or
  traumatizing. The GM will describe it. Take \forward{-1}.
\end{amove}

\begin{amove}{Barkskin}
  So long as your feet touch the ground you have \armor{+1}.
\end{amove}

\begin{amove}{Eyes of the Tiger}
  When you \condition{mark an animal (with mud, dirt, or blood)} you
  can see through that animal’s eyes as if they were your own, no
  matter what distance separates you. Only one animal at a time may be
  marked in this way.
\end{amove}

\begin{amove}{Shed}
  When you \condition{take damage while shapeshifted} you may choose
  to revert to your natural form to negate the damage.
\end{amove}

\begin{amove}{Thing-Talker}
  You see the spirits in the sand, the sea and the stone. You may now
  apply your \move{Spirit Tongue}, \move{Shapeshifter} and
  \move{Studied Essence} to inanimate natural objects (plants and
  rocks) or creatures made thereof, as well as animals. Thing-talker
  forms can be exact copies or can be mobile vaguely humanoid-shaped
  entities.
\end{amove}

\begin{amove}{Formcrafter}
  When you use \move{Shapeshifter} choose a stat: you take
  \ongoing{+1} to rolls using that stat while shifted. The GM will
  choose a stat, too: you take \ongoing{-1} to rolls using that stat
  while shifted.
\end{amove}

\begin{amove}{Elemental Mastery}
  When you \condition{call on the primal spirits of fire, water, earth
    or air to perform a task for you}, roll +WIS. \onSuccess, choose
  two. \onPartial, choose one. \onMiss, some catastrophe occurs as a
  result of your calling.

  \begin{itemize}
  \item The effect you desire comes to pass
  \item You avoid paying nature’s price
  \item You retain control
  \end{itemize}
\end{amove}

\begin{amove}{Balance}
  When you deal damage, take 1 balance. When you touch someone and
  channel the spirits of life you may spend balance. For each balance
  spent, heal 1d4 HP.
\end{amove}


\vfill\null
\columnbreak

\secondAdvances

\begin{amove}{Embracing No Form}
  When you use \move{Shapeshifter}, roll 1d4 and add that total to your hold.
\end{amove}


\begin{amove}{Doppelgänger’s Dance}
  You are able to study the essence of specific individuals to take
  their exact form, including men, elves, or the like. Suppressing
  your tell is possible, but if you do, take \ongoing{-1} until you
  return to your own form.
\end{amove}

\begin{amove}{Blood and Thunder}
\moveReplaces{Red of Tooth and Claw}

  When you are in an appropriate animal form (something dangerous)
  increase your damage to d10.
\end{amove}

\begin{amove}{The Druid Sleep}
  When you take this move, the next opportunity that you have safety
  and time to spend in an appropriate location, you may attune
  yourself to a new land. This effect occurs only once and the GM will
  tell you how long it will take and what cost you must pay. From then
  on, you are considered to be born of the soil in both lands.
\end{amove}

\begin{amove}{World-Talker}
  \moveRequires{Thing-Talker}

  You see the patterns that make up the fabric of the world. You may
  now apply your \move{Spirit Tongue}, \move{Shapeshifter} and
  \move{Studied Essence} moves to pure elements—fire, water, air and
  earth.
\end{amove}

\begin{amove}{Stalker’s Sister}
  Choose one move from the ranger class list.
\end{amove}

\begin{amove}{Formshaper}
  \moveRequires{Formcrafter}

  You may increase your armor by 1 or deal an additional +1d4 damage
  while in an animal form. Choose which when you use
  \move{Shapeshifter}.
\end{amove}

\begin{amove}{Chimera}
  When you use \move{Shapeshifter}, you may create a merged form of up to
  three different shapes. You may be a bear with the wings of an eagle
  and the head of a ram, for example. Each feature will grant you a
  different move to make. Your chimera form follows the same rules as
  \move{Shapeshifter} otherwise.
\end{amove}

\begin{amove}{Weather Weaver}
  When you are \condition{under open skies when the sun rises} the GM
  will ask you what the weather will be that day. Tell them whatever
  you like, it comes to pass.
\end{amove}


\vfill\null
\end{multicols}

\end{document}
