\documentclass[8pt]{extarticle}
\input{assets/prelude}

% Modify this commands to define Class name, Base HP, Base Load and Damage Dice (only number)
\pbClass{Fighter}
\pbBaseHP{10}
\pbDamage{10}

\pbNames{Dwarf}{Ozruk, Surtur, Brunhilda, Annika, Janos, Greta, Dim,
  Rundrig, Jarl, Xotoq}

\pbNames{Elf}{Elohiir, Sharaseth, Hasrith, Shevaral, Cadeus, Eldar,
  Kithracet, Thelian}

\pbNames{Halfling}{Finnegan, Olive, Randolph, Bartleby, Aubrey,
  Baldwin, Becca}

\pbNames{Human}{Hawke, Rudiger, Gregor, Brianne, Walton, Castor,
  Shanna, Ajax, Hob}

\pbLook{Hard Eyes, Dead Eyes, or Eager Eyes}
\pbLook{Wild Hair, Shorn Hair, or Battered Helm}
\pbLook{Calloused Skin, Tanned Skin, or Scarred Skin}
\pbLook{Built Body, Lithe Body, or Ravaged Body}

\begin{document}

\charbanner

\begin{minipage}[t]{3.2in}
\leftbanner{Folk}

\begin{optfeature}{Dwarf}
  When you \textbf{share a drink with someone}, you may \move{Parley}
  with them using CON instead of CHA.
\end{optfeature}

\begin{optfeature}{Elf}
  Choose one weapon—you can always treat weapons of that type as if
  they had the \itag{precise} tag.
\end{optfeature}

\begin{optfeature}{Halfling}
  When you \move{Defy Danger} and \textbf{use your small size to your
    advantage}, take +1.
\end{optfeature}

\begin{optfeature}{Human}
  Once per battle you may reroll a single damage roll (yours or
  someone else’s).
\end{optfeature}

\ 

\leftbanner{Alignment}

\begin{optfeature}{Good}
  Defend those weaker than you.
\end{optfeature}

\begin{optfeature}{Neutral}
  Defeat a worthy opponent.
\end{optfeature}

\begin{optfeature}{Evil}
  Kill a defenseless or surrendered enemy.
\end{optfeature}


\ 

\leftbanner{Bonds}

\vfill\null
\end{minipage}
\begin{minipage}[t]{4.6in}

\rightbanner{Starting Moves}

\begin{basicmove}{Bend Bars, Lift Gates}
  When you \condition{use pure strength to destroy an inanimate obstacle},
  roll +STR. \onSuccess, choose 3. \onPartial, choose 2.

  \begin{itemize}
  \item It doesn’t take a very long time
  \item Nothing of value is damaged
  \item It doesn’t make an inordinate amount of noise
  \item You can fix the thing again without a lot of effort
  \end{itemize}
\end{basicmove}
\

\begin{basicmove}{Armored}
  You ignore the \itag{clumsy} tag on armor you wear.
\end{basicmove}
\


\begin{basicmove}{Signature Weapon}
  This is your weapon. There are many like it, but this one is
  yours. Your weapon is your best friend. It is your life. You master
  it as you master your life. Your weapon, without you, is
  useless. Without your weapon, you are useless. You must wield your
  weapon true.

  Choose a base description, all are 2 weight:

  \begin{choices}
  \item Sword
  \item Axe
  \item Hammer
  \item Spear
  \item Flail
  \item Fists
  \end{choices}

  Choose the range that best fits your weapon:

  \begin{choices}
  \item \itag{hand}
  \item \itag{close}
  \item \itag{reach}
  \end{choices}

  Choose two enhancements:

  \begin{choices}
  \item Hooks and spikes. \ntag{+1}{damage}, but \ntag{+1}{weight}.
  \item Sharp. \ntag{+2}{piercing}.
  \item Perfectly weighted. Add \itag{precise}.
  \item Serrated edges. \ntag{+1}{damage}.
  \item Glows in the presence of one type of creature, your choice.
  \item Huge. Add \itag{messy} and \itag{forceful}.
  \item Versatile. Choose an additional range.
  \item Well-crafted. \ntag{-1}{weight}.
  \end{choices}


  Choose a look:

  \begin{choices}
  \item Ancient
  \item Unblemished
  \item Ornate
  \item Blood-stained
  \item Sinister
  \end{choices}

\end{basicmove}

\vfill\null
\end{minipage}

\charlower
\clearpage

\gearbanner

\begin{multicols}{2}

  \begin{quote}

    \yourLoad{12}. You carry your signature weapon and dungeon rations
    (\ntag{5}{uses}, \ntag{1}{weight}). Choose your defenses:

    \begin{choices}
    \item Chainmail (\ntag{1}{armor}, \ntag{1}{weight}) and
      adventuring gear (\ntag{1}{weight})
    \item Scale armor (\ntag{2}{armor}, \ntag{3}{weight})
    \end{choices}

    Choose two:

    \begin{choices}
    \item 2 Healing potions (\ntag{0}{weight})
    \item Shield (\ntag{+1}{armor}, \ntag{2}{weight})
    \item Antitoxin (\ntag{0}{weight}), dungeon rations
      (\ntag{1}{weight}), and poultices and herbs (\ntag{1}{weight})
    \item 22 coins
    \end{choices}

\end{quote}

\ 

\columnbreak

\ 

\end{multicols}

\widebanner{Advanced Moves}

\begin{multicols}{2}
\firstAdvances

\begin{amove}{Merciless}
  When you deal damage, deal \damage{+1d4}.
\end{amove}

\begin{amove}{Heirloom}
  When you \condition{consult the spirits that reside within your
    signature weapon}, they will give you an insight relating to the
  current situation, and might ask you some questions in return,
  roll +CHA. \onSuccess, the GM will give you good detail. \onPartial,
  the GM will give you an impression.
\end{amove}

\begin{amove}{Armor Mastery}
  When you \condition{make your armor take the brunt of damage dealt
    to you}, the damage is negated but you must reduce the armor value
  of your armor or shield (your choice) by 1. The value is reduced
  each time you make this choice. If the reduction leaves the item
  with 0 armor it is destroyed.
\end{amove}

\begin{amove}{Improved Weapon}
  Choose one extra enhancement for your signature weapon.
\end{amove}

\begin{amove}{Seeing Red}
  When you \move{Discern Realities} during combat, you take +1.
\end{amove}

\begin{amove}{Interrogator}
  When you \move{Parley} using threats of impending violence as
  leverage, you may use STR instead of CHA.
\end{amove}

\begin{amove}{Scent of Blood}
  When you \move{Hack and Slash} an enemy, your next attack against
  that same foe deals \damage{1d4}.
\end{amove}

\begin{amove}{Multiclass Dabbler}
  Get one move from another class. Treat your level as one lower for
  choosing the move.
\end{amove}

\begin{amove}{Iron Hide}
  You gain \armor{+1}.
\end{amove}

\begin{amove}{Blacksmith}
  When you have access to a forge you can graft the magical powers of
  a weapon onto your signature weapon. This process destroys the
  magical weapon. Your signature weapon gains the magical powers of
  the destroyed weapon.
\end{amove}


\vfill\null
\columnbreak

\secondAdvances

\begin{amove}{Bloodthirsty}
  \moveReplaces{Merciless}

  When you deal damage, deal \damage{+1d8}.
\end{amove}

\begin{amove}{Armored Perfection}
  \moveReplaces{Armor Mastery}

  When you choose to let your armor take the brunt of damage dealt to
  you, the damage is negated and you take \forward{+1} against the
  attacker, but you must reduce the armor value of your armor or
  shield (your choice) by 1. The value is reduced each time you make
  this choice. If the reduction leaves the item with 0 armor it is
  destroyed.
\end{amove}

\begin{amove}{Evil Eye}
\moveRequires{Seeing Red}

  When you \condition{enter combat}, roll +CHA. \onSuccess, hold
  2. \onPartial, hold 1. Spend your hold to make eye contact with an
  NPC present, who freezes or flinches and can’t act until you break
  it off. \onMiss, your enemies immediately identify you as their
  biggest threat.
\end{amove}

\begin{amove}{Taste of Blood}
  \moveReplaces{Scent of Blood}

  When you \move{Hack and Slash} an enemy, your next attack against
  that same foe deals \damage{+1d8}.
\end{amove}

\begin{amove}{Multiclass Initiate}
  \moveRequires{Multiclass Dabbler}

  Get one move from another class. Treat your level as one lower for
  choosing the move.
\end{amove}

\begin{amove}{Steel Hide}
  \moveReplaces{Iron Hide}

  You gain \armor{+2}.
\end{amove}

\begin{amove}{Through Death’s Eyes}
  When you \condition{go into battle}, roll +WIS. \onSuccess, name
  someone who will live and someone who will die. \onPartial, name
  someone who will live or someone who will die. Name NPCs, not player
  characters. The GM will make your vision come true, if it’s even
  remotely possible. \onMiss, you see your own death and consequently
  take \ongoing{-1} throughout the battle.
\end{amove}

\begin{amove}{Eye for Weaponry}
  When you \condition{look over an enemy’s weaponry}, ask the GM how
  much damage they do.
\end{amove}

\begin{amove}{Superior Warrior}
  When you \move{Hack and Slash}, \onMassiveSuccess, you deal your
  damage, avoid their attack, and impress, dismay, or frighten your
  enemy.
\end{amove}


\vfill\null
\end{multicols}

\end{document}
