\documentclass[8pt]{extarticle}
\input{assets/prelude}

% Modify this commands to define Class name, Base HP, Base Load and Damage Dice (only number)
\pbClass{Paladin}
\pbBaseHP{10}
\pbDamage{10}

\pbNames{Human}{Thaddeus, Augustine, Lux, Cassius, Hadrian, Lucia,
  Octavia, Regulus, Valeria, Sanguinus, Titanius}

\pbLook{Kind Eyes, Fiery Eyes, or Glowing Eyes}
\pbLook{Helmet, Styled Hair, or Bald}
\pbLook{Worn Holy Symbol or Fancy Holy Symbol}
\pbLook{Fit Body, Bulky Body, or Thin Body}

\begin{document}

\charbanner

\begin{minipage}[t]{3.2in}
\leftbanner{Folk}

\begin{optfeature}{Human}
  When you \condition{pray for guidance, even for a moment, and ask,
    ``What here is evil?''} the GM will tell you, honestly.
\end{optfeature}

\ 

\leftbanner{Alignment}

\begin{optfeature}{Lawful}
  Deny mercy to a criminal or unbeliever.
\end{optfeature}

\begin{optfeature}{Good}
  Endanger yourself to protect someone weaker than you.
\end{optfeature}

\ 

\leftbanner{Bonds}

\vfill\null
\end{minipage}
\begin{minipage}[t]{4.6in}


\rightbanner{Starting Moves}

\begin{basicmove}{Lay on Hands (CHA)}
  When you \condition{touch someone, skin to skin, and pray for their
    well-being}, roll +CHA. \onSuccess, you heal 1d8 damage or remove
  one disease. \onPartial, they are healed, but the damage or disease
  is transferred to you.
\end{basicmove}
\

\begin{basicmove}{Armored}
  You ignore the \itag{clumsy} tag on armor you wear.
\end{basicmove}
\

\begin{basicmove}{I Am the Law}
  When you \condition{give an NPC an order based on your divine
    authority}, roll +CHA. \onPartial, they choose one:

  \begin{itemize}
  \item Do what you say
  \item Back away cautiously, then flee
  \item Attack you
  \end{itemize}

  \onSuccess, you also take \forward{+1} against them. \onMiss, they
  do as they please and you take \forward{-1} against them.
\end{basicmove}
\

\begin{basicmove}{Quest}
  When you \condition{dedicate yourself to a mission through prayer
    and ritual cleansing}, state what you set out to do:

  \begin{itemize}
  \item Slay \blank, a great blight on the land
  \item Defend \blank\ from the iniquities that beset them
  \item Discover the truth of \blank
  \end{itemize}

  Then choose up to two boons:

  \begin{itemize}
  \item An unwavering sense of direction to \blank
  \item Invulnerability to \blank\ (e.g., edged weapons, fire, enchantment, etc.)
  \item A mark of divine authority
  \item Senses that pierce lies
  \item A voice that transcends language
  \item A freedom from hunger, thirst, and sleep
  \end{itemize}

  The GM will then tell you what vow or vows is required of you to
  maintain your blessing:

  \begin{itemize}
  \item Honor (forbidden: cowardly tactics and tricks)
  \item Temperance (forbidden: gluttony in food, drink, and pleasure of the flesh)
  \item Piety (required: observance of daily holy services)
  \item Valor (forbidden: suffering an evil creature to live)
  \item Truth (forbidden: lies)
  \item Hospitality (required: comfort to those in need, no matter who they are)
  \end{itemize}

\end{basicmove}



\vfill\null
\end{minipage}
\charlower
\clearpage

\gearbanner

\begin{multicols}{2}

  \begin{quote}
    \yourLoad{12}. You start with dungeon rations
    (\ntag{5}{uses}, \ntag{1}{weight}), scale armor (\ntag{2}{armor},
    \ntag{3}{weight}), and some mark of faith, describe it
    (\ntag{0}{weight}). Choose your weapon:

    \begin{choices}
    \item Halberd (\itag{reach}, \ntag{+1}{damage}, \itag{two-handed},
      \ntag{2}{weight})
    \item Long sword (\itag{close}, \ntag{+1}{damage},
      \ntag{1}{weight}) and shield (\ntag{+1}{armor},
      \ntag{2}{weight})
    \end{choices}

  Choose one:

  \begin{choices}
  \item Adventuring gear (\ntag{1}{weight})
  \item Dungeon rations (\ntag{1}{weight}) and healing potion (\ntag{0}{weight})
  \end{choices}

\end{quote}

\ 

\columnbreak

\ 

\end{multicols}

\widebanner{Advanced Moves}

\begin{multicols}{2}

\firstAdvances

\begin{amove}{Divine Favor}
  Dedicate yourself to a deity (name a new one or choose one that’s
  already been established). You gain the \move{Commune} and
  \move{Cast a Spell} Cleric moves. When you select this move, treat
  yourself as a Cleric of level 1 for using spells. Every time you
  gain a level thereafter, increase your effective cleric level by 1.
\end{amove}

\begin{amove}{Bloody Aegis}
  When you \condition{take damage} you can grit your teeth and accept
  the blow. If you do you take no damage but instead suffer a debility
  of your choice. If you already have all six debilities you can’t use
  this move.
\end{amove}

\begin{amove}{Smite}
  While on a \move{Quest} you deal +1d4 damage.
\end{amove}

\begin{amove}{Exterminatus}
  When you \condition{speak aloud your promise to defeat an enemy},
  you deal +2d4 damage against that enemy and -4 damage against anyone
  else. This effect lasts until the enemy is defeated. If you fail to
  defeat the enemy or give up the fight, you can admit your failure,
  but the effect continues until you find a way to redeem yourself.
\end{amove}

\begin{amove}{Charge!}
  When you \condition{lead the charge into combat}, those you lead
  take \forward{+1}.
\end{amove}

\begin{amove}{Staunch Defender}
  When you \move{Defend} you always get +1 hold, even on a 6-.
\end{amove}

\begin{amove}{Setup Strike}
  When you \move{Hack and Slash}, choose an ally. Their next attack
  against your target does +1d4 damage.
\end{amove}

\begin{amove}{Holy Protection}
  You get \ntag{+1}{armor} while on a \move{Quest}.
\end{amove}

\begin{amove}{Voice of Authority}
  Take +1 to order hirelings.
\end{amove}

\begin{amove}{Hospitaller}
  When you \condition{heal an ally}, you heal +1d8 damage.
\end{amove}


\vfill\null
\columnbreak

\secondAdvances

\begin{amove}{Evidence of Faith}
\moveRequires{Divine Favor}

  When you \condition{see divine magic as it happens}, you can ask the
  GM which deity granted the spell and its effects. Take +1 when
  acting on the answers.
\end{amove}

\begin{amove}{Holy Smite}
\moveReplaces{Smite}

  While on a \move{Quest} you deal +1d8 damage.
\end{amove}

\begin{amove}{Ever Onward}
  \moveReplaces{Charge!}

  When you \condition{lead the charge into combat}, those you lead
  take \forward{+1} and \armorForward{+2}.
\end{amove}

\begin{amove}{Impervious Defender}
  \moveReplaces{Staunch Defender}

  When you \move{Defend} you always get +1 hold, even on a
  6-. \onMassiveSuccessFor{Defend}, instead of getting hold the
  nearest attacking creature is stymied giving you a clear advantage,
  the GM will describe it.
\end{amove}

\begin{amove}{Tandem Strike}
  \moveReplaces{Setup Strike}

  When you \move{Hack and Slash}, choose an ally. Their next attack
  against your target does \damage{+1d4} and they take \forward{+1}
  against them.
\end{amove}

\begin{amove}{Divine Protection}
  \moveReplaces{Holy Protection}

  You get \ntag{+2}{armor} while on a \move{Quest}.
\end{amove}

\begin{amove}{Divine Authority}
  \moveReplaces{Voice of Authority}

  Take +1 to order hirelings. \onMassiveSuccess, the hireling
  transcends their moment of fear and doubt and carries out your order
  with particular effectiveness or efficiency.
\end{amove}

\begin{amove}{Perfect Hospitaller}
  \moveReplaces{Hospitaller}

  When you \condition{heal an ally}, you heal \damage{+2d8}.
\end{amove}

\begin{amove}{Indomitable}
  When you suffer a debility (even through \move{Bloody Aegis}) take
  \forward{+1} against whatever caused it.
\end{amove}

\begin{amove}{Perfect Knight}
  When you \move{Quest} you choose three boons instead of two.
\end{amove}


\vfill\null
\end{multicols}

\end{document}
